---
title: "p8105_hw1_zc2610"
output: github_document
date: "2022-09-19"
---
```{r}
library(tidyverse)
```

# Problem 1 
```{r}
data("penguins", package = "palmerpenguins")
```
Description:

1. This dataset contains 8 variables in total: species,island,bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g,sex,year
2. This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns of data

# Problem 2
```{r create a data frame}
  problem2_df = 
  tibble(
  norm = rnorm(n = 10),
  logical = norm > 0,
  character_vector = c("1","2","3","4","5","6","7","8","9","10"),
  factor_vector = factor(c("first","first","first","second","second","second","second","second","third","third"))
  )
```
```{r mean of each variable}
mean(pull(problem2_df, norm))
mean(pull(problem2_df, logical))
mean(pull(problem2_df, character_vector))
mean(pull(problem2_df, factor_vector))
```
According to the output of code above, we can learn that "norm" and "logical" variable can output the mean
because their arguments are numeric or logical. "character_vector" and "factor_vector" doesn't work with the mean and return NA since arguments are not numeric or logical


